Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-21 paper/paper.tex
case study in progress

Then, we encode our observations, based on which we want to
solve the dilemma:

@@

>>>>

Then, we record our observations, based on which we want to
solve the dilemma:

@@

\begin{lstlisting}[style=default]
(def samples (doquery :lmh deli nil))

(def N 1000)
(def predicts (map get-predicts (take N (drop N samples))))

(def p-same+ (/ (count (filter :same-customer predicts)) (double N)))

;; single customer                      
(def time-to-arrive+ (map :time-to-arrive (filter :same-customer predicts)))
(def mean-to-arrive+ (mean time-to-arrive+))
(def sd-to-arrive+ (std time-to-arrive+))

;; two customers
(def times-to-arrive+ (map :times-to-arrive 
                           (filter (complement :same-customer) predicts)))
(def mean-1-to-arrive+ (mean (map first times-to-arrive+)))
(def sd-1-to-arrive+ (std (map first times-to-arrive+)))
(def mean-2-to-arrive+ (mean (map second times-to-arrive+)))
(def sd-2-to-arrive+ (std (map second times-to-arrive+)))

(def samples (doquery :bbvb deli nil))

(clojure.pprint/pprint (anglican.bbvb/get-variational (nth samples N)))
\end{lstlisting}

\begin{figure}
    \includegraphics[trim={12pt 0 0 0},scale=0.7]{same-customer-time.pdf}
\end{figure}

\begin{figure}
    \includegraphics[trim={12pt 0 0 0},scale=0.7]{different-customers-times.pdf}
\end{figure}

\begin{verbatim}
{S28219
 {(0 anglican.runtime.flip-distribution)
  {:p 0.11671977016875924,
   :dist
   {:min 0.0,
    :max 1.0}}},
 S28209
 {(0 anglican.runtime.normal-distribution)
  {:mean 10.99753360180663,
   :sd 0.7290976433082352}},
 S28217
 {(0 anglican.runtime.normal-distribution)
  {:mean 12.668050292254202,
   :sd 0.9446695174790353}},
 S28215
 {(0 anglican.runtime.normal-distribution)
  {:mean 9.104132559955836,
   :sd 0.9479290526821788}}}
\end{verbatim}
